\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{SAGAR GUPTA} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 9752646915 \\ Morena, MP} 
\address{\href{sagar2003gupta@gmail.com}{sagar2003gupta@gmail.com} \\ 
\href{https://www.linkedin.com/in/sagar-gupta2201/}{linkedin.com/in/sagar} \\ \href{https://github.com/decoder2201}{github.com/sagar}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\large E\small ducation}

{\bf GLA University}  \hfill Mathura, UP, India \\
 {\textit{Bachelor of Computer Science} \hfill {2020 - 2024}
 }
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{\large T\small ECHNICAL \large S\small KILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: & Java, JavaScript, HTML, CSS
\\
Libraries/Frameworks: & React.js, Node.js, Express.js\\
Databases: & MongoDB\\
Developer Tools: & Git, VS Code, Intellij, Sublime Text 

\end{tabular}\\
\end{rSection}

\begin{rSection}{\large E\small XPERIENCE}

\textbf{Front end development intern} \hfill Oct 2023 - Nov 2023\\
\textit{Cod Soft}
 \begin{itemize}
    \itemsep -2pt {} 
     \item Leveraged JavaScript and React to develop and deploy user-friendly frontend projects.
     \item Demonstrated adeptness in real-time problem-solving and bug resolution.
 \end{itemize}
 
\textbf{Web development intern} \hfill Jul 2022 - Aug 2022\\ \textit{Code Decoder Developer}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Wroked on React.js, MongoDB, Express.js and Node.js.
     \item Proficient in resolving bugs, optimizing UI components, and managing databases.
    \item Recognized with a letter of recommendation for outstanding performance.
 \end{itemize}
 
\textbf{Web/Android development intern} \hfill Apr 2022 - Jul 2022\\ \textit{Net Camp Solutions Private LTD.}
 \begin{itemize}
    \itemsep -2pt {} 
     \item Developed Android applications using Core Java, showcasing in mobile development.
     \item Excelled UI enhancement, and database management for seamless project execution.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\large P\small ROJECTS} 
\vspace{-1.25em}
\item \textbf{Fresh News} {\textit{$|$ React.js, Web API} \hfill Apr 2023 - May 2023}
\begin{itemize}
    \itemsep -1pt {} 
     \item Crafted a responsive React JS-based news website with dynamic content fetched from a web API, offering seamless navigation through categories like technology and politics. Developed intuitive interface with filtering options for personalized browsing experience.
 \end{itemize}

\item \textbf{Fame} {\textit{$|$ React.js, Node.js, Express.js, MongoDB} \hfill Jan 2023 - Mar 2023} 
\begin{itemize}
    \itemsep -2pt {} 
     \item Designed and executed a full-stack social media clone using React JS, Node JS, and MongoDB, replicating essential features of major platforms.
     \item Integrated WebSocket technology into the MERN stack for real-time chat application, enabling instant message delivery and sharing data functionality.
 \end{itemize}
 
\item \textbf{Shop It} {\textit{$|$ React.js, Node.js, Express.js, MongoDB} \hfill Oct 2022 - Dec 2022} 
\begin{itemize}
    \itemsep -2pt {} 
     \item Developed with an immersive e-commerce platform, using React JS for frontend and Node JS for backend, offering dynamic category selection for personalized shopping experiences across electronics, fashion, and children's items.
     \item Crafted a visually appealing interface with the help of backend system that optimizes product presentation based on user preferences.
 \end{itemize}
\end{rSection} 

\end{document}
